Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-24 main.tex
Some progress in taint

>>>>

\leo{Rough draft/take on this section}
\begin{itemize}
\item Taint tracking is an interesting property.
\item It's weaker than traditional noninterference, but easier to enforce so people use it.
\item \leo{Some of the intuition from below}
\end{itemize}

\paragraph{Taint Tracking Property}

Given a contour C and pair of traces $\overline{M}$ and $\overline{N}$,
the pair of contoured trace $\overline(C, M)_n$ and $\overline(C,N)_n$ is in the
taint tracking contour-lockstep hyperproperty if:
\begin{itemize}
\item For all $0 \leq i < m$ the restriction of the trace to its
  length $i$ prefix is in the standard noninterference property
  \leo{Defined in the previous section}, where $m$ is the minimum
  index (or infinity) for which $PC(M_i) \not = PC(N_i)$ or
  $instr(M_i) \not = instr(N_i)$.
\end{itemize}

\paragraph{Taint Tracking Policy}

\newcommand*{\clean}{{\em clean}}
\newcommand*{\tainted}{{\em tainted}}
\newcommand*{\boring}{{\em boring}}
\begin{itemize}
\item We define three {\em tags} \leo{have we defined what these
  are?}: \clean, \tainted, and \boring. Machine components tagged
  \clean by the policy represent protected locations that should never
  be tainted. Components tagged \tainted are either sources of taint
  (e.g. network inputs) or components that have been influenced by
  other \tainted ones. Finally \boring components are locations that
  are allowed to become tainted (perhaps temporarily) but have not
  yet.
\end{itemize}
